Article 2:	Information-Seeking Behaviors for Information on Covid-19 Vaccinations

### 2022-01-25 paper2.Rmd
Discussion Done

---
title: "Article 2:	Information-Seeking Behavior Decision-Making between Online Search and Interpersonal Networks: The Case of Covid-19 Vaccinations "
author: "Kelsey Gonzalez"
date: "`r format(Sys.time(), '%d %B, %Y')`"
editor_options:
  chunk_output_type: console
output:
  bookdown::pdf_document2: 
    latex_engine: xelatex
    number_sections: true
  bookdown::word_document2: 
    toc: true
    reference_docx: StylesTemplate.docx
header-includes:
   - \usepackage{siunitx}
   - \usepackage{setspace}
   - \usepackage{dcolumn}
   - \usepackage{caption}
   - \usepackage{longtable}
   - \usepackage{booktabs}
   - \doublespacing
   - \usepackage{placeins}
csl: american-sociological-association.csl
bibliography: "My Library.bib"
indent: true
---

@@

# Abstract 
How do individuals perform information search, and what factors help them decide
which information search vehicle to utilize, such as interpersonal networks or
online tools, I investigate the above question using individual survey data of
934 Adults in the United States and find that X and Y. Furthermore, this paper
demonstrates that searching for a question online using a search engine or
social network was more common than traditional means of information gathering,
such as network activation (asking someone in their social network for
informational support). Using X and Y theory I predict that that few people will
activate their social network for informational support in my chosen case of
Covid-19 vaccinations because of the social cost of doing so but fail to find
evidence for this thesis. I also investigate which information channels are
associated with vaccinations against the virus, and find that social netwokring
sites are associated with lower rates. I also find important ethnocracial
differences in information search vehicles utilization and vaccination
reception.

@@

Information is especially important given the prominent trends of
misinformation, disinformation, and mistrust in traditional institutions
[@starbird19; @kata10]. While no belief in false information can be thought of as
harmless [@douglas21] some discredited theories such as 'vaccines cause autism'
have major ramifications for both the individual and the social world that
surrounds them. For example, a new found public resistance to vaccination
against Measles by so-called 'anti-vaxxers' caused a 17% increase in rates
worldwide in 2019. This increase killed  142,000 people, most of whom were
children under the age of five [@givetash19]. However, even in the ever-evolving
research agenda of misinformation, much of the research focuses on spaces where
individual first come into contact with conspiracy theories or other information
rather than what individuals do with the information they obtain
[@johnsonOnlineCompetitionPro2020; @broniatowski_etal20]. 
<!-- cite something else here -->

The lack of research in this area makes it quite unclear how individuals choose
to search for information through the multimedia environment of the 21st
century. Even outside of the misinformation literature, much of the research
conducted in social networks and communication focus on senders, influencers,
and persuasion strategies [@mertonManifestLatentFunctions1968;
@katzPersonalInfluencePart1955; @lazarsfeldPeopleChoice1944 ], rather than on
“the receiver as an active information seeker and processor."   [@johnsonComprehensiveModelCancerRelated1993].

@@

## subheading - how people search

Active directed searching by individuals to obtain information is sparsely
discussed in the sociological literature. Pejtersen
[-@pejtersenDesignComputeraidedUsersystem1984], a scholar of library and
information science, theorized that there are 5 strategies for searching for
information. The most common strategy is browsing, where people follow leads
based on associations without planning ahead. Another strategy is analytical,
which includes an explicit consideration of all facets of the question to guide
a search. The empirical method guides the search based on tactics that were
successful in past research. The known site strategy is to go to the direct
source of the information if known. And finally, the similarity method is to
find information based on another similar question that already has an answer.
These 5 strategies vary in their demands for prior knowledge, cognitive
processing, memory, and time spent. While this theory is aimed at finding
information in a library setting, scholars have extended the theory to other
fields and validated the framework [@fidelHumanInformationInteraction2012]; the
frame is a useful beginning point for my theories of information search through
network activation or through computer-mediated communication.

@@

One way to find information is to activate network ties to find out information
through a form of social support. Social support, while previously used
interchangeably with the term social networks and social integration
[@houseStructuresProcessesSocial1988], are the emotional, informational, and
instrumental assistance functions performed between social ties and have strong
and measurable association with health outcomes
[@houseMeasuresConceptsSocial1985; @thoitsMechanismsLinkingSocial2011].
Informational support is the process of seeking “help in defining,
understanding, and coping with problematic events and include education, advice,
or referral to another source of support” [@winemiller_etal93, p. 640].
Brashers, a health communications researcher, defines informational support
slightly differently, focusing on the exchange of information that “facilitates
coping with life stresses… that may be exchanged among members of a support
network” [-@brashersInformationSeekingAvoiding2002, p. 260] <!--  Both of these
definitions provide important lenses for my question of how computer-mediated or
interpersonal information-seeking strategies vary.--> If information is needed
but there is no search for coping or deeper understanding of important matters,
people are likely to choose to search online.

@@

However, informational support can also be sought outside of the social network
context, namely via computer-mediated information search tools such as the
process of “Googling”. As the online environment began penetrating all facets of
modern human life, it makes sense that performing online search has become one
of the most convenient vehicles for information search. While Small
[-@smallSomeoneTalk2017] focuses on how support can depend on a network tie
simply "happened to be there", online search is theoretically the most
frictionless and costless mode of support. There are three computer-mediated
vehicles I consider for this analysis: search engines like Google, posting
questions on online forums like subreddits or Facebook groups, and posting a
status update online via Facebook or Twitter. The first two comprise what I call
“online search”, while the third is conceptually distinct and important to
include in the survey; yet, it is a hybrid of social network activation and
online search.

@@

As online search or interaction also allows increased anonymity, no or lowered
social cost, and the potential avoidance of embarrassment and other negative
social interactions, I theorize that a majority of people who searched for
information will have done so online.

@@

# Research Methodology
The data used for this research project are based on original survey data
sampled between `r format( min(rain$date), '%B %d, %Y')`  through 
`r format(max(rain$date), '%B %d, %Y')`. This survey was hosted on Qualtrics and
participants were paid and recruited using Amazon Turk (MTurk). The total valid
survey responses (_n_ = `r nrow(rain)`) were selected from a total of 1,066
respondents; some responses were disqualified due to a few factors such as
detected usage of a VPN, random answer clicking (determined by illogical
responses), poor quality typed responses (e.g. social network alters
consistently named random nouns), or taking the survey more than once. The same
is slighted gender unbalanced, slightly skewing towards a male sample. For the
respondents who provided their zipcode (p = 
`r round(nrow(rain[!is.na(rain$region),]) / nrow(rain), 2)`), the 
sample is quite balanced with a slight skew towards MTurkers in the South (p = 
`r round(nrow(rain[rain$region == 'South',]) / nrow(rain), 2)`). 
The survey took an average of `r round(mean(rain$duration), 2)` minutes with a 
standard deviation of `r round(sd(rain$duration), 2)` minutes. The shortest 
valid survey took `r round(min(rain$duration), 2)` minutes and the longest took 
`r round(max(rain$duration), 2)` minutes. Participants were paid \$6.00 for their 
time after Amazon administrative fees, funded by a Grant awarded to Kelsey E.
Gonzalez and Nicolas Legewie by the Summer Institute in Computational Social
Science and the Russell Sage Foundation. The main portion of this survey
replicates the book, Someone to Talk To [@smallSomeoneTalk2017] by expanding on
Small’s finding that people draw on much broader sources than “important people”
for support by segregating weak-tie social support into instrumental, emotional,
and informational support (see House et al. 1988)). The latter part of the
survey focuses on resource activation for the specific case-study of information
during the Covid-19 pandemic and is analyzed in this paper.

@@

datasummary(formula = 
  (`Received info` = receive_i) +
    (`Received info, Doctor` = receive_i_fr_dr) +
    (`Received info, Person` = receive_i_fr_pers) +
    (`Received info, News` = receive_i_fr_tv) +
    (`Received info, Social Networking Site` = receive_i_fr_onlnet) +
    (`Received info, Online Forum` = receive_i_fr_onlgroup) +
    (`Sought Info` = int_sought) +
    (`Sought Info, Doctor` = int_sought_fr_dr) +
    (`Sought Info, Person` = int_sought_fr_pers) +
    (`Sought Info, Social Networking Site` = int_sought_fr_onlnet) +
    (`Sought Info, Online Forum` = int_sought_fr_onlgroup) +
    (`Sought Info, Online Search` = int_sought_fr_onlsearch) +
    (`Vaccination Status` = vacc_status) +
    (`Vaccination Favorability` = vacc_view_pos) +
    (`Age` = age) +
    (`Hispanic or Latino/x` = hispanic) +
    (`Race, Black` = race_white) +
    (`Race, Black` = race_black) +
    (`Race, Native American` = race_nat) +
    (`Race, Asian or Pacific Islander` = race_asian) +
    (`Associate's Deg or above` = college)  ~ 
    (Mean + SD) ,
  data = desc_table,
  fmt = '%.2f',
  title = 'Descriptive Statistics for Dichotomous and Numeric Variables',
  notes =c(glue("Notes: {nrow(rain)} Surveyed, Conducted {format( min(rain$date), '%B %d')} through {format(max(rain$date), '%B %d')}, 2021.")),
  output = "kableExtra") %>% 
  kable_styling(latex_options = c("hold_position", "striped"))

@@

Further dependent variables segment the above question into multiple options;
"How did you look for information about the Covid-19 vaccine?". Respondents were
posed with 5 responses and 'other', of which they could select multiple. The
largest proportion, `r print_perc(rain$int_sought_fr_dr)`, asked their 
'doctor or another health professional' (95% Confidence Interval = 
\{`r conf_int_prop(rain$int_sought_fr_dr)`\}).
About `r print_perc(rain$int_sought_fr_pers)`  said they asked 'a person 
like friend, neighbor, or family member that [they] know' (95% Confidence 
Interval = \{`r conf_int_prop(rain$int_sought_fr_pers)`\}). An additional
`r print_perc(rain$int_sought_fr_onlsearch)` searched 'for [their] question 
using an online search engine such as Google or Bing' (95% Confidence Interval 
= \{`r conf_int_prop(rain$int_sought_fr_onlsearch)`\}). About a quarter of the 
sample, `r print_perc(rain$int_sought_fr_onlgroup)`, 'posted queries in an 
online discussion group, listserve, or other online forum like a Facebook Group 
or Subreddit' (95% Confidence Interval = \{`r conf_int_prop(rain$int_sought_fr_onlgroup)`\}).
And finally, `r print_perc(rain$int_sought_fr_onlnet)` of the sample 'posted queries 
on a social networking site such as Facebook timeline, Twitter status update, or 
Linkedin' (95% Confidence Interval = \{`r conf_int_prop(rain$int_sought_fr_onlnet)`\}).
Much of the question wording and the specific categories of search were inspired
by ICPSR project 37220 [@scanlon19].

@@

datasummary(formula = (
  # (`Income` = income)+  
                         (`Gender` = gender)+  
                         (`Highest Education Level` = educ) + 
                         (`Plan to be Vaccinated if not` = vacc_status_future)  +
                         (`Found Info Sought Useful` = int_sought_useful) +
                         (`Census Region` = region)) ~ N + Percent(), 
 data = rain,
   fmt = '%.2f',
  title = 'Descriptive Statistics for Categorical Variables',
 notes =c(glue("Notes: {nrow(rain)} Surveyed, Conducted {format( min(rain$date), '%B %d')} through {format(max(rain$date), '%B %d')}, 2021.")),
 output = "kableExtra") %>%
  kable_styling(latex_options = c("hold_position", "striped"))

@@

```{r}
vacc_status_freq <- rain[!is.na(rain$vacc_status_future),] %>% 
  group_by(col = vacc_status_future) %>% 
  summarise(n = n()) %>%
  mutate(n = n / sum(n))
```
Another Dependent variable for this analysis is a dichotomous variable
indicating whether the respondent has received a vaccination against Covid-19 or
plans to. For this survey, the number of doses were unimportant and actually
having already received the dose were irrelevant to the research question. This
variable instead focuses on intent or opinion about the vaccine. About 
`r print_perc(rain$vacc_view_pos)` have a positive view about the vaccine. This
construct is made through the combination of  two survey items. The first item
is actual vaccination status, obtained through the question 'Did you receive a
Covid-19 vaccine?'. `r print_perc(rain$vacc_status)` of the sample said that
they had indeed received a vaccination (95% Confidence Interval = \{
`r conf_int_prop(rain$vacc_status)`\}). As the national vaccination rate is
closer to 55% (CITE), this indicates some bias in our sample that must be
acknowledged: either MTurkers are more likely to be vaccinated that the normal
population (sampling bias) or there is some conformity bias in the responses
causing survey takers to provide false answers. The second survey item that
contributes to 'Vaccination Outlook' was only given to those who had not
responded 'yes' to the to their vaccination status. These respondents were asked 'Do you
plan to receive a vaccine for the prevention of the Covid-19 virus?'. Of those
who were asked this question (n = `r nrow(rain[!is.na(rain$vacc_status_future),])`),
`r label_percent()(filter(vacc_status_freq, col == 'Definitely yes') %>% pull(n))`
said they were 'definitely yes' getting the vaccine; 
`r label_percent()(filter(vacc_status_freq, col == 'Probably yes') %>% pull(n))` 
said they were 'probably yes' going to receive vaccine. The rest of the sample was more unsure: 
`r label_percent()(filter(vacc_status_freq, col == 'Might or might not') %>% pull(n))`
said they 'Might or might not', 
`r label_percent()(filter(vacc_status_freq, col == 'Probably not') %>% pull(n))`
said 'Probably not', and finally
`r label_percent()(filter(vacc_status_freq, col == 'Definitely not') %>% pull(n))`
said they would 'definitely not' receive the vaccine. The variable 'Vaccination
Outlook' indicates their either the respondent received a Covid-19 vaccine or
either probably or definitely will in the future.

### Independent Variables
The first independent variables used in this analysis are based on the question, 
'In the past 12 months, without searching for it, did you receive information
about the Covid-19 vaccine from … (check all sources you received information
from)'. This differs from the 'How did you look for information' question above
because it is based on passive reception of information. The largest proportion
of respondents had received information from a person like friend, neighbor, or
family member that [they] know ($\widehat{p}$ = `r print_perc(rain$receive_i_fr_pers)`
). Respondents also commonly received information from a television news channel
or a newspaper, about `r print_perc(rain$receive_i_fr_tv)` of the sample.
`r print_perc(rain$receive_i_fr_dr)` of the sample had received information from
their doctor or other health professional while `r print_perc(rain$receive_i_fr_onlnet)` 
received information from a social networking site such as Facebook timeline,
Twitter status update, or linkedin. Finally, the lowest proportion of the sample
had received information from an online discussion group, listserve, or other
online forum like a Facebook group or subreddit 
($\widehat{p}$ = `r print_perc(rain$receive_i_fr_onlgroup)`).

We also asked various demographic questions to understand our sample. The 
average age of our sample was `r round(mean(rain$age, na.rm = T), 2)`. 
Our sample was `r label_percent()(nrow(filter(rain, gender == "Female")) / nrow(rain))`
female, and `r label_percent()(nrow(filter(rain, gender == "Male")) / nrow(rain))`
male. The sample is diverse racially though some ethnic groups are under
represented compared to national averages. Race was evaluated using the
question, 'What is your race? If you are "mixed race", select all that apply.'
Because of the multi-selection question, each variable is dichotomous and
proportions are shown. `r print_perc(rain$race_white)` of the sample claimed
they were 'White', `r print_perc(rain$race_black)` claimed to be 'Black or
African American', `r print_perc(rain$race_nat)` chose 'American Indian or
Alaskan Native', `r print_perc(rain$race_asian)` selected 'Asian', and finally 
when asked ' Are you Hispanic, Latino/a/x, or Latin American Origin?', 
`r print_perc(rain$hispanic)` selected 'Yes'. Respondents were also asked to 
select the  highest level of education that you have completed. Based on the 
breakdown between 'Less than high school', 'High school graduate', 'Some college',
'Associate's or Technical degree', 'Bachelor's degree', and 'Graduate or 
professional degree',  `r print_perc(rain$college)` of the sample were classified
to have a College-level education (Associate's degree or above).

@@

My analytic strategy proceeds in four steps. In Tables \@ref(tab:table-1-desc) 
& \@ref(tab:table-2-desc), I present descriptive statistics for all study 
variables, including variable ranges, means, and standard deviations. For this 
paper, I rely heavily on logistic regression, modeled in `r`; specifically, I 
fit a series of Binomial Generalized Linear Models [@venables2002a]. In Table \@ref(tab:table-model-1)^[All tables in this paper were created with the modelsummary package in `r` [@modelsummary] ]
, I fit a logistic regression model predicting
whether someone sought information about Covid-19 using their sources of
information ('Received info') as well as various demographic variables such as
age, education level and race. Figure \@ref(fig:plot-model-1) then illustrates
the relationship between the coefficients and information seeking.^[Figures in 
this paper were all created using the `r` packages jtools [@jtools] and ggplot2 [@wickham_etal; @wickham11] ].
In Table \@ref(tab:model-2-phi) I disaggregate information seeking behaviors by
investigating the difference in proportions of each of the 5 different avenues
of seeking information about Covid-19: from another person, from a doctor, on an
online forum, on a social networking site, or using an online search tool. I
investigate these differences through a phi coefficient [@warrens08], otherwise
known as a mean square contingency coefficient which is used to investigate the
degree of association between two binary variables. ^[To calculate the Phi
Coefficient, I utilize the Psych `r` package [@psych] ] I then investiage the
associations between my predictors and the 5 information search vehicles by
modelling a series of logistic regressions in Table \@ref(tab:table-model-2).
Finally, in Table \@ref(tab:table-model-3), I investigate whether there is a
relationship between information receiving and information seeking behaviors and
the choice to get vaccinated against Covid-19 through a logistic regression
model predicting Vaccination Outlook.  Figure \@ref(fig:plot-model-3) then
illustrates the relationship between the coefficients and vaccination outlook.

@@

In academia and policy, the main focus is on the information that is sent to
consumers, seeing people as passive receivers of information. My dissertation
instead focuses on individuals as active agents in their search for information
which helps me uncover the information individuals are exposed to. By looking at
how individuals search, I aim to identify pain points and focus areas for future
interventions in the misinformation process.

@@

@@

\newpage
# Appendix 1: Survey Questions

>>>>

---
title: "Article 2:	Information-Seeking Behaviors for Information on Covid-19 Vaccinations"
author: "Kelsey Gonzalez"
date: "`r format(Sys.time(), '%d %B, %Y')`"
editor_options:
  chunk_output_type: console
output:
  bookdown::word_document2: 
    toc: true
    reference_docx: StylesTemplate.docx
  bookdown::pdf_document2:
    latex_engine: xelatex
    number_sections: true
header-includes:
   - \usepackage{siunitx}
   - \usepackage{setspace}
   - \usepackage{dcolumn}
   - \usepackage{caption}
   - \usepackage{longtable}
   - \usepackage{booktabs}
   - \doublespacing
   - \usepackage{placeins}
csl: american-sociological-association.csl
bibliography: "My Library.bib"
indent: true
always_allow_html: true
---

@@

# Abstract 
How do individuals perform information search, and what factors help them decide
which information search vehicle to utilize, such as interpersonal networks or
online tools, I investigate the above question using individual survey data of
934 Adults in the United States and find that X and Y. Furthermore, this paper
demonstrates that searching for a question online using a search engine or
social network was more common than traditional means of information gathering,
such as network activation (asking someone in their social network for
informational support). Using X and Y theory I predict that that few people will
activate their social network for informational support in my chosen case of
Covid-19 vaccinations because of the social cost of doing so but fail to find
evidence for this thesis. I also investigate which information channels are
associated with vaccinations against the virus and find that social networking
sites are associated with lower rates. I also find important ethnoracial
differences in information search vehicles utilization and vaccination
reception.

@@

Information is especially important given the prominent trends of
misinformation, disinformation, and mistrust in traditional institutions
[@starbird19; @kata10]. While no belief in false information can be thought of as
harmless [@douglas21] some discredited theories such as 'vaccines cause autism'
have major ramifications for both the individual and the social world that
surrounds them. For example, a newfound public resistance to vaccination
against Measles by so-called 'anti-vaxxers' caused a 17% increase in rates
worldwide in 2019. This increase killed  142,000 people, most of whom were
children under the age of five [@givetash19]. However, even in the ever-evolving
research agenda of misinformation and infodemiology [@eysenbach02], much of the
research focuses on the supply side of information, like spaces where
individuals first encounter with conspiracy theories or other information
[@johnsonOnlineCompetitionPro2020; @broniatowski_etal20].
<!-- cite something else here -->

The lack of research in this area makes it quite unclear how individuals choose
to search for information through the multimedia environment of the 21st
century. Even outside of the misinformation literature, much of the research
conducted in social networks and communication focus on senders, influencers,
and persuasion strategies [@mertonManifestLatentFunctions1968;
@katzPersonalInfluencePart1955; @lazarsfeldPeopleChoice1944 ], rather than on
“the receiver as an active information seeker and processor."   [@johnsonComprehensiveModelCancerRelated1993; though there are always exceptions 
@eysenbach09].

@@

## Information Search

Active directed searching by individuals to obtain information is sparsely
discussed in the sociological literature. Pejtersen
[-@pejtersenDesignComputeraidedUsersystem1984], a scholar of library and
information science, theorized that there are 5 strategies for searching for
information. The most common strategy is browsing, where people follow leads
based on associations without premeditation. Another strategy is analytical,
which includes an explicit consideration of all facets of the question to guide
a search. The empirical method guides the search based on tactics that were
successful in past research. The known site strategy is to go to the direct
source of the information if known. And finally, the similarity method is to
find information based on another similar question that already has an answer.
These 5 strategies vary in their demands for prior knowledge, cognitive
processing, memory, and time spent. While this theory is aimed at finding
information in a library setting, scholars have extended the theory to other
fields and validated the framework [@fidelHumanInformationInteraction2012]; the
frame is a useful beginning point for my theories of information search through
network activation or through computer-mediated communication.

@@

One way to find information is to activate network ties to find out information
through a form of social support. Social support, while previously used
interchangeably with the term social networks and social integration
[@houseStructuresProcessesSocial1988], are the emotional, informational, and
instrumental assistance functions performed between social ties and have strong
and measurable association with health outcomes
[@houseMeasuresConceptsSocial1985; @thoitsMechanismsLinkingSocial2011].
Informational support is the process of seeking “help in defining,
understanding, and coping with problematic events and include education, advice,
or referral to another source of support” [@winemiller_etal93, p. 640].
Brashers, a health communications researcher, defines informational support
slightly differently, focusing on the exchange of information that “facilitates
coping with life stresses… that may be exchanged among members of a support
network” [-@brashersInformationSeekingAvoiding2002, p. 260]. <!--  Both of these
definitions provide important lenses for my question of how computer-mediated or
interpersonal information-seeking strategies vary.--> If information is needed
but there is no search for coping or deeper understanding of important matters,
people are likely to choose to search online.

@@

However, informational support can also be sought outside of the social network
context, namely via computer-mediated information search tools such as the
process of “Googling”. As the online environment began penetrating all facets of
modern human life, it makes sense that performing online search has become one
of the most convenient vehicles for information search. While Small
[-@smallSomeoneTalk2017] focuses on how support can depend on a network tie
simply "happened to be there", online search is theoretically the most
frictionless and costless mode of support. There are three computer-mediated
vehicles I consider for this analysis: search engines like Google, posting
questions on online forums like subreddits or Facebook groups, and posting a
status update online via Facebook or Twitter. The first two comprise what I call
“online search”, while the third is conceptually distinct and important to
include in the survey; yet it is a hybrid of social network activation and
online search.

@@

As online search or interaction also allows increased anonymity, no or lowered
social cost, and the potential avoidance of embarrassment and other negative
social interactions, I theorize that most people who searched for
information will have done so online.

@@

# Research Methodology
The data used for this research project are based on original survey data
sampled between `r format( min(rain$date), '%B %d, %Y')`  through 
`r format(max(rain$date), '%B %d, %Y')`. This survey was hosted on Qualtrics and
participants were paid and recruited using Amazon Turk (MTurk). The total valid
survey responses (_n_ = `r nrow(rain)`) were selected from a total of 1,066
respondents; some responses were disqualified due to a few factors such as
detected usage of a VPN, random answer clicking (determined by illogical
responses), poor quality typed responses (e.g., social network alters
consistently named random nouns), or taking the survey more than once. The same
is slighted gender unbalanced, slightly skewing towards a male sample. For the
respondents who provided their zip code (p = 
`r round(nrow(rain[!is.na(rain$region),]) / nrow(rain), 2)`), the 
sample is quite balanced with a slight skew towards MTurkers in the South (p = 
`r round(nrow(rain[rain$region == 'South',]) / nrow(rain), 2)`). 
The survey took an average of `r round(mean(rain$duration), 2)` minutes with a 
standard deviation of `r round(sd(rain$duration), 2)` minutes. The shortest 
valid survey took `r round(min(rain$duration), 2)` minutes and the longest took 
`r round(max(rain$duration), 2)` minutes. Participants were paid \$6.00 for their 
time after Amazon administrative fees, funded by a Grant awarded to Kelsey E.
Gonzalez and Nicolas Legewie by the Summer Institute in Computational Social
Science and the Russell Sage Foundation. The main portion of this survey
replicates the book, Someone to Talk To [@smallSomeoneTalk2017] by expanding on
Small’s finding that people draw on much broader sources than “important people”
for support by segregating weak-tie social support into instrumental, emotional,
and informational support [see @houseStructuresProcessesSocial1988]. The latter
part of the survey focuses on resource activation for the specific case-study of
information during the Covid-19 pandemic analyzed in this paper.

@@

datasummary(formula = 
  (`Received info` = receive_i) +
    (`Received info, Doctor` = receive_i_fr_dr) +
    (`Received info, Person` = receive_i_fr_pers) +
    (`Received info, News` = receive_i_fr_tv) +
    (`Received info, Social Networking Site` = receive_i_fr_onlnet) +
    (`Received info, Online Forum` = receive_i_fr_onlgroup) +
    (`Sought Info` = int_sought) +
    (`Sought Info, Doctor` = int_sought_fr_dr) +
    (`Sought Info, Person` = int_sought_fr_pers) +
    (`Sought Info, Social Networking Site` = int_sought_fr_onlnet) +
    (`Sought Info, Online Forum` = int_sought_fr_onlgroup) +
    (`Sought Info, Online Search` = int_sought_fr_onlsearch) +
    (`Vaccination Status` = vacc_status) +
    (`Vaccination Favorability` = vacc_view_pos) +
    (`Age` = age) +
    (`Hispanic or Latino/x` = hispanic) +
    (`Race, White` = race_white) +
    (`Race, Black` = race_black) +
    (`Race, Native American` = race_nat) +
    (`Race, Asian or Pacific Islander` = race_asian) +
    (`Associate's Deg or above` = college)  ~ 
    (Mean + SD) ,
  data = desc_table,
  fmt = '%.2f',
  title = 'Descriptive Statistics for Dichotomous and Numeric Variables',
  notes =c(glue("Notes: {nrow(rain)} Surveyed, Conducted {format( min(rain$date), '%B %d')} through {format(max(rain$date), '%B %d')}, 2021.")),
  output = "kableExtra") %>% 
  kable_styling(latex_options = c("hold_position", "striped"))

@@

Further dependent variables segment the above question into multiple options;
"How did you look for information about the Covid-19 vaccine?". Respondents were
posed with 5 responses and 'other', of which they could select multiple. The
largest proportion, `r print_perc(rain$int_sought_fr_dr)`, asked their 
'doctor or another health professional' (95% Confidence Interval = 
\{`r conf_int_prop(rain$int_sought_fr_dr)`\}).
About `r print_perc(rain$int_sought_fr_pers)` said they asked, 'a person 
like friend, neighbor, or family member that [they] know' (95% Confidence 
Interval = \{`r conf_int_prop(rain$int_sought_fr_pers)`\}). An additional
`r print_perc(rain$int_sought_fr_onlsearch)` searched 'for [their] question 
using an online search engine such as Google or Bing' (95% Confidence Interval 
= \{`r conf_int_prop(rain$int_sought_fr_onlsearch)`\}). About a quarter of the 
sample, `r print_perc(rain$int_sought_fr_onlgroup)`, 'posted queries in an 
online discussion group, listserve, or other online forum like a Facebook Group 
or Subreddit' (95% Confidence Interval = \{`r conf_int_prop(rain$int_sought_fr_onlgroup)`\}).
And finally, `r print_perc(rain$int_sought_fr_onlnet)` of the sample 'posted queries 
on a social networking site such as Facebook timeline, Twitter status update, or 
LinkedIn' (95% Confidence Interval = \{`r conf_int_prop(rain$int_sought_fr_onlnet)`\}).
Much of the question wording and the specific categories of search were inspired
by ICPSR project 37220 [@scanlon19].

@@

datasummary(formula = ((`Gender` = gender)+  
                         (`Highest Education Level` = educ) + 
                         (`Plan to be Vaccinated if not` = vacc_status_future)  +
                         (`Found Info Sought Useful` = int_sought_useful) +
                         (`Census Region` = region)) ~ N + Percent(), 
            data = rain,
            fmt = '%.2f',
            title = 'Descriptive Statistics for Categorical Variables',
            notes =c(glue("Notes: {nrow(rain)} Surveyed, Conducted {format( min(rain$date), '%B %d')} through {format(max(rain$date), '%B %d')}, 2021.")),
            output = "kableExtra") %>%
  kable_styling(latex_options = c("hold_position", "striped"))

@@

```{r}
vacc_status_freq <- rain[!is.na(rain$vacc_status_future),] %>% 
  group_by(col = vacc_status_future) %>% 
  summarise(n = n()) %>%
  mutate(n = n / sum(n))
```
Another Dependent variable for this analysis is a dichotomous variable
indicating whether the respondent has received a vaccination against Covid-19 or
plans to. For this survey, the number of doses or timeline of receipt were less
relevant to the research question. This variable instead focuses on intent or
opinion about the vaccine. About `r print_perc(rain$vacc_view_pos)` have a
positive view about the vaccine. This construct is made through the combination
of  two survey items. The first item is actual vaccination status, obtained through 
the question 'Did you receive a Covid-19 vaccine?'.
`r print_perc(rain$vacc_status)` of the sample said that
they had indeed received a vaccination (95% Confidence Interval = \{`r conf_int_prop(rain$vacc_status)`\}). As the national vaccination rate is
closer to 55% (CITE), this indicates some bias in our sample that must be
acknowledged: either MTurkers are more likely to be vaccinated that the normal
population (sampling bias) or there is some conformity bias in the responses
causing survey takers to provide false answers. The second survey item that
contributes to 'Vaccination Outlook' was only given to those who had not
responded 'yes' to the to their vaccination status. These respondents were asked 'Do you
plan to receive a vaccine for the prevention of the Covid-19 virus?'. Of those
who were asked this question (n = `r nrow(rain[!is.na(rain$vacc_status_future),])`),
`r label_percent()(filter(vacc_status_freq, col == 'Definitely yes') %>% pull(n))`
said they were 'definitely yes' getting the vaccine; 
`r label_percent()(filter(vacc_status_freq, col == 'Probably yes') %>% pull(n))` 
said they were 'probably yes' going to receive vaccine. The rest of the sample was more unsure: 
`r label_percent()(filter(vacc_status_freq, col == 'Might or might not') %>% pull(n))`
said they 'Might or might not', 
`r label_percent()(filter(vacc_status_freq, col == 'Probably not') %>% pull(n))`
said 'Probably not', and finally
`r label_percent()(filter(vacc_status_freq, col == 'Definitely not') %>% pull(n))`
said they would 'definitely not' receive the vaccine. The variable 'Vaccination
Outlook' indicates that either the respondent received a Covid-19 vaccine or
either probably or definitely will in the future.

### Independent Variables
The first independent variables used in this analysis are based on the question, 
'In the past 12 months, without searching for it, did you receive information
about the Covid-19 vaccine from … (check all sources you received information
from)'. This differs from the 'How did you look for information' question above
because it is based on passive reception of information. The largest proportion
of respondents had received information from a person like friend, neighbor, or
family member that [they] know ($\widehat{p}$ = `r print_perc(rain$receive_i_fr_pers)`
). Respondents also commonly received information from a television news channel
or a newspaper, about `r print_perc(rain$receive_i_fr_tv)` of the sample.
`r print_perc(rain$receive_i_fr_dr)` of the sample had received information from
their doctor or other health professional while `r print_perc(rain$receive_i_fr_onlnet)` 
received information from a social networking site such as Facebook timeline,
Twitter status update, or LinkedIn. Finally, the lowest proportion of the sample
had received information from an online discussion group, listserve, or other
online forum like a Facebook group or subreddit 
($\widehat{p}$ = `r print_perc(rain$receive_i_fr_onlgroup)`).

We also asked various demographic questions to understand our sample. The 
average age of our sample was `r round(mean(rain$age, na.rm = T), 2)`. 
Our sample was `r label_percent()(nrow(filter(rain, gender == "Female")) / nrow(rain))`
female, and `r label_percent()(nrow(filter(rain, gender == "Male")) / nrow(rain))`
male. The sample is diverse racially though some ethnic groups are underrepresented compared to national averages. Race was evaluated using the
question, 'What is your race? If you are "mixed race", select all that apply.'
Because of the multi-selection question, each variable is dichotomous and
proportions are shown. `r print_perc(rain$race_white)` of the sample claimed
they were 'White', `r print_perc(rain$race_black)` claimed to be 'Black or
African American', `r print_perc(rain$race_nat)` chose 'American Indian or
Alaskan Native', `r print_perc(rain$race_asian)` selected 'Asian', and finally 
when asked, 'Are you Hispanic, Latino/a/x, or Latin American Origin?', 
`r print_perc(rain$hispanic)` selected 'Yes'. Respondents were also asked to 
select the  highest level of education that you have completed. Based on the 
breakdown between 'Less than high school', 'High school graduate', 'Some college',
'Associate's or Technical degree', 'Bachelor's degree', and 'Graduate or 
professional degree',  `r print_perc(rain$college)` of the sample were classified
to have a college-level education (Associate's degree or above).

@@

My analytic strategy proceeds in four steps. In Tables \@ref(tab:table-1-desc) 
& \@ref(tab:table-2-desc), I present descriptive statistics for all study 
variables, including variable ranges, means, and standard deviations. For this 
paper, I rely heavily on logistic regression, modeled in `r`; specifically, I 
fit a series of Binomial Generalized Linear Models [@venables2002a]. In Table \@ref(tab:table-model-1)^[All tables in this paper were created with the modelsummary package in `r` [@modelsummary] ]
, I fit a logistic regression model predicting
whether someone sought information about Covid-19 using their sources of
information ('Received info') as well as various demographic variables such as
age, education level and race. Figure \@ref(fig:plot-model-1) then illustrates
the relationship between the coefficients and information seeking.^[Figures in 
this paper were all created using the `r` packages jtools [@jtools] and ggplot2 [@wickham_etal; @wickham11] ].
In Table \@ref(tab:model-2-phi) I disaggregate information seeking behaviors by
investigating the difference in proportions of each of the 5 different avenues
of seeking information about Covid-19: from another person, from a doctor, on an
online forum, on a social networking site, or using an online search tool. I
investigate these differences through a phi coefficient [@warrens08], otherwise
known as a mean square contingency coefficient which is used to investigate the
degree of association between two binary variables. ^[To calculate the Phi
Coefficient, I utilize the Psych `r` package [@psych] ] I then investigate the
associations between my predictors and the 5 information search vehicles by
modelling a series of logistic regressions in Table \@ref(tab:table-model-2).
Finally, in Table \@ref(tab:table-model-3), I investigate whether there is a
relationship between information receiving and information seeking behaviors and
the choice to get vaccinated against Covid-19 through a logistic regression
model predicting Vaccination Outlook.  Figure \@ref(fig:plot-model-3) then
illustrates the relationship between the coefficients and vaccination outlook.

@@

In academia and policy, the focus is on the information that is sent to
consumers, seeing people as passive receivers of information. My dissertation
instead focuses on individuals as active agents in their search for information
which helps me uncover the information individuals are exposed to. By looking at
how individuals search, I aim to identify pain points and focus areas for future
interventions in the misinformation process.

@@

\newpage

@@

\newpage

# Appendix 1: Survey Questions
